The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
fst spatial threshold interpretation

output: 
    bookdown::word_document2
    # github_document

@@

#### Interpretations:

@@

>>>>

output: 
    # bookdown::word_document2
    github_document

@@

@@

(ref:socres) : varying scale in social threshold. For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

```{r, fig.cap='(ref:socres)'}
knitr::include_graphics('../graphics/figure-spatialthreshold.png')
```
